Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-10-30 paper/paper.qmd
Made more changes to paper

## Outcome variables

TO-DO: All variables should be thoroughly examined and explained.

@@

TO-DO: All variables should be thoroughly examined and explained.

@@

## Model set-up

# Results {#sec-results}

@@

# Idealized Methodology

## Sampling Approach

@@

The survey will begin by introducing each potential participant to the topic and providing necessary context about the purpose of the research. This introduction aims to make the participants feel informed and comfortable with the process. The first question will ask whether the individual is willing to participate in the survey, emphasizing that participation is voluntary. It will also be clearly communicated that respondents may drop out of the survey at any point if they choose. Once participants agree, they will proceed to answer a series of demographic questions that will help ensure a diverse and stratified sample. These questions include:

>>>>

## Outcome variables
We aim to predict our response variable `candidate_trump`, which is a binary variable with 0 and 1 representing a loss and win in a state respectively. The plot of our outcome variables is shown below:
```{r}

```

@@

TO-DO: All variables should be thoroughly examined and explained.
[PLOTS OF PREDICTOR VARIABLES NEEDED]
- **Sample Size (`sample_size`)**: The number of respondents in the poll.
- **State (`state`)**: A categorical variable for different U.S. states.
- **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset).
- **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data.

@@

## Model set-up
A Bayesian approach is used in constructing our model. As such, an informative prior is assumed, and logistic regression is implemented due to the nature of the outcome variable (binary).

The predictor variables used in the model are as follows:

- **Sample Size (`sample_size`)**: The number of respondents in the poll.
- **State (`state`)**: A categorical variable for different U.S. states.
- **Days to Election (`days_to_election`)**: Counts the number of days until Election Day starting from today’s date (it also uses `end_date` from the original dataset).
- **Voter Percentage of Candidate (`pct`)**: A continuous variable for the percentage of voters who plan to vote for Trump based on polling data.

The model takes the form of the following equation [TO-DO]:
\begin{align}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
\epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align}

Where: 
\begin{align}
\beta_0 & \text{ is the intercept term} \\
\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
\sigma^2 & \text{ is the variance of the error term}
\end{align}

## Interpretation
[WORDS TO-DO]

## Model Justification and Evaluation
[tbl-summary] shows the summary table for the model. 
F1-Score blabla

# Results {#sec-results}
[WORDS]

@@

# Appendix B: Idealized Methodology and Survey

## Sampling Approach and Strategy

@@

### Stratification Variables [TO-DO]
* **Age Groups**: 18-29, 30-44, 45-64, 65+ 
* **Gender**: Male, Female, Non-binary/Other 
* **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other 
* **Education Level**: No high school, High school graduate, College graduate, Post-graduate 
* **Income Bracket**: <$30,000, \$30,000-\$60,000, \$60,000-\$100,000, >\$100,000 
* **Geographic Region**: Northeast, Midwest, South, West

## Budget Allocation
* **Marketing and Outreach (Ads and Incentives)**: \$50,000

* **Survey Design and Data Validation**:
  - Questionnaire Development: \$5,000
  - Pilot Testing (survey run on small group of people): \$5,000
  - Google Forms (with built-in validation rules): \$5,000

* **Data Analysis and Software**: 
  - Statistical Software: \$5,000
  - Staff Fees (Analysts and Statisticians): \$15,000

* **Financial Incentives**: \$2,000
* **Miscellaneous Expenses and Contingency Fund**: \$8,000

###  **Survey Structure**:
The survey will begin by introducing each potential participant to the topic and providing necessary context about the purpose of the research. This introduction aims to make the participants feel informed and comfortable with the process. The first question will ask whether the individual is willing to participate in the survey, emphasizing that participation is voluntary. It will also be clearly communicated that respondents may drop out of the survey at any point if they choose. Once participants agree, they will proceed to answer a series of demographic questions that will help ensure a diverse and stratified sample. These questions include:
